Portfolios of fishing permits and species reduce risk but adjusting fishing strategy is risky

### 2016-08-16 portfolio/text/anderson-etal-rev-pfx.tex
Develop text
Start adding affiliations

\title{Benefits and costs of income diversification for 
  Alaskan fishermen
\ldots}
\author{
Sean C. Anderson, 
\ldots}
\date{}

@@

>>>>

\title{Portfolios of fishing permits and species
reduce risk but adjusting fishing strategy is risky}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson
}

\date{}

@@

\noindent
$^1$School of Aquatic and Fishery Sciences, Box 355020,
University of Washington, Seattle, WA 98195, USA

\noindent
$^2$Conservation Biology Division, Northwest Fisheries Science Center,
National Marine Fisheries Service, National Oceanographic and
Atmospheric Administration, 2725 Montlake Blvd E, Seattle, WA 98112, USA

\noindent
$^5$Alaska Fisheries Science Center,
National Marine Fisheries Service, National Oceanographic and
Atmospheric Administration, Bldg 4,
7600 Sand Point Way NE, Seattle, WA, 98115, USA

\noindent
Affiliations \ldots
